<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Using interactiveDisplayBase for Bioconductor object visualization and modification}
-->

```{r setup, echo=FALSE}
suppressWarnings(suppressPackageStartupMessages(library(knitr)))
options(width=80)
```

```{r wrap-hook, echo=FALSE}
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

```{r interactiveDisplayBase-load, echo=FALSE}
suppressWarnings(suppressPackageStartupMessages(library(interactiveDisplayBase)))
```

# interactiveDisplayBase

[interactiveDisplayBase](http://bioconductor.org/packages/2.13/bioc/html/interactiveDisplayBase.html)

`interactiveDisplayBase` uses the function `display()` to host a browser based 
application on the fly using the Shiny package.  Shiny UI elements are available based on the 
object passed to `display()`.  These allow the user to modify how the plot is 
displayed, and for some objects, modify or subset the data and send it back to 
the console.

## Methods


Many of the display method will have a button that allows you return
subset values back to the R session.  To use these, couple the intial
call with an assignment operator like this:

```{r dataframe_demo, eval=FALSE}
mtcars2 <- display(mtcars)
```

Once you leave the diplay web gui, the results of the above
interaction will be captured inside of mtcars2.


## Acknowledgments

Shiny <br/>
Joe Cheng and Winston Chang <br/>
http://www.rstudio.com/shiny/ <br/>

Force Layout <br/>
Jeff Allen <br/>
https://github.com/trestletech/shiny-sandbox/tree/master/grn <br/>

gridSVG <br/>
Simon Potter <br/>
http://sjp.co.nz/projects/gridsvg/ <br/>

Zoom/Pan JavaScript libraries <br/>
John Krauss <br/>
https://github.com/talos/jquery-svgpan <br/>
Andrea Leofreddi <br/>
https://code.google.com/p/svgpan/ <br/>

JavaScript Color Chooser <br/>
Jan Odvarko <br/>
http://jscolor.com/ <br/>

Data-Driven Documents <br/>
Michael Bostock <br/>
http://d3js.org/ <br/>

Javascript for returning values from data.frames <br/>
Kirill Savin <br/> 

Help with the display method for data.frames <br/>
Dan Tenenbaum <br/>
